An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/eval.tex
config: eval done

\item Whether \app can successfully 
  detect real-world configuration errors?

\item Whether \app can correctly detect anomalous values?

\item How long do training and verification last?

@@

\subsection{\app's Effectiveness}

We now apply \app to check against real-world misconfiguration problems.
We use a real misconfiguration dataset~\cite{xu15hey}
that are collected from several online forums, \eg, 
Stack Overflow and MySQL forum.
Each configuration file in this dataset was posted by 
programmers or system administrators, 
when they confront the misconfiguration issues in practice.
This dataset contains 261 incorrect MySQL configuration files.

@@

\subsection{Detecting Anomalous Values}

@@

\subsection{The Run-Time of Verification}

\ennan{Here, we need three pictures. In the first figure, x-axis should
be the number (or the size) of entries in the training dataset, and 
y-axis should be the run-time of parsing. In the second figure,
we need to measure the time of generating rules. }

>>>>

\item Whether \app can successfully 
  detect real-world configuration errors ($\S$\ref{subsec-effectiveness})?

\item Whether \app can correctly detect anomalous values
($\S$\ref{subsec-anomalous})?

\item How long do training and verification last ($\S$\ref{subsec-time})?

@@

\subsection{\app's Effectiveness}
\label{subsec-effectiveness}

We now apply \app to check against real-world misconfiguration problems.
We use a real misconfiguration dataset~\cite{configdataset}
that are collected from several online forums, \eg, 
Stack Overflow and MySQL forum.
Each configuration file in this dataset was posted by 
programmers or system administrators, 
when they confront the misconfiguration issues in practice.
This dataset contains 261 incorrect MySQL configuration files.

@@

\subsection{Detecting Anomalous Values}
\label{subsec-anomalous}

@@

\subsection{Training \& Verification Performance}
\label{subsec-time}

We run our experiments measuring the run-time of training and
verification of \app.
Our experiments were run on a machine equipped with
64-bit Intel Core i7-4790 CPU @ 3.60GHz and 8 GB of RAM.

\para{Training performance.}
We first evaluate the training time of \app. Namely, how long
does \app need to use to generate rules.
We vary the number of configuration files in our training dataset
between 10 and 200, and record the corresponding time.
Table~\ref{table-training} presents our evaluational results.
We found the training time of \app is acceptable in practice,
because 150 files in the training dataset have been able to make
us obtain good enough rules.
For 150 files, \app only needs about 7 minutes.
Furthermore, even if we train \app with a 200-file dataset,
we need less than 15 minutes, but such a training dataset
can generate about 200,000 rules.

\para{Verification performance.}
We also measure the verification time of \app, and found
the verification time is very fast. With 232,613 rules,
\app needs less than one second to verify a MySQL configuration file.
\app only needs 3 minutes to finish the verifications to
the real-world dataset~\cite{configdataset}, we used to 
evaluate the effectiveness of \app,
which contains 261 misconfiguration files.

\begin{table}[t]
\centering
\caption{Training time for different datasets}
\label{table-training}
\begin{tabular}{|c|c|}
\hline
{\bf The \# of Files for Training}       & {\bf Training Time (sec.)}  \\ 
\hline
\hline
10   & 2.997        \\ \hline
50   & 46.4208          \\ \hline
100  & 206.7798       \\ \hline
150  & 431.7772        \\ \hline
200  & 856.6383  \\ 
\hline
\end{tabular}
\end{table}
